
---
classoption: landscape
output:
  html_document:
    fig_width: 11
    keep_md: yes
  pdf_document: default
  word_document: default
---


  
```{r, echo = FALSE, message = FALSE, warning = FALSE}
load(file="Random data with and without ans options.RData")
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
library(pander)
library(plyr)

```


```{r, echo=FALSE, eval=TRUE, results = "asis"}
# Create a function that produces a list with the required statistics for each item, this is used in displaying the tables and the plots per answer option


retrieve <- function(results, n = NULL, sub.cat){
  if(sub.cat){
    list2env(results[[n]], envir  = globalenv())
  } else {
    list2env(results, envir  = globalenv())
  }          
}

if(is.list(results[[1]])) sub.cat = TRUE else sub.cat = FALSE

retrieve(results, n = 1, sub.cat) # Get objects in list to global environment

CreateItemList <- function(input.correct, n.answer.op, freq.answer.op = NULL, perc.answer.op = NULL, answer.op.tot.cor = NULL, item.sum = NULL, item.perc = NULL, item.tot.cor = NULL){
  # Creates a list with frequency, percentage correct, and IRC for every item.
  # 
  # Args:
  #  input.correct: Matrix with [i,j]  the score of student i on item j
  #  n.answer.op: Vector with number of answer options per question
  #  freq.answer.op: Matrix with [i,j] the frequency of answer option i of item j
  #  perc.answer.op: Matrix with [i,j] the percentage of answer option i of item j
  #  answer.op.tot.cor: Matrix with [i,j] the item total correlation for answer option i of item j
  #  item.sum: Vector with total number correct per item
  #  item.perc: Vector with percentage correct per item
  #  item.tot.cor: Vector with item rest correlation per item
  #
  # Returns: 
  #  A list with frequency, percentage and IRC for total and each answer options (if answer options exist).
  
  item.names <- colnames(input.correct)
  
  item.list <- list() # Creates list to put item output in
  colnames1 <- c(" ", "frequency", "percentage", "IRC")
  colnames2 <- c("answer.option", "frequency", "percentage", "IRC", "Correct")
  

  
  for (i in 1:n.item) {
    if (n.answer.op[i] > 0) {
      Correct <- c(ifelse(key[1:n.answer.op[i], i] == 1, "Correct", "Incorrect"), "Incorrect")
      
      # Frequency is also stored at this point, but not used.
      # in case someone wants to alter the script to display the frequency instead of the percentage
      item.list[[i]] <- data.frame(c(LETTERS[1:n.answer.op[i]], "Missing"),
                                   c(freq.answer.op[c(2:(n.answer.op[i] + 1), 1), i]),
                                   c(perc.answer.op[c(2:(n.answer.op[i] + 1), 1), i]),
                                   c(answer.op.tot.cor[c(2:(n.answer.op[i] + 1), 1), i]),
                                   Correct,
                                   row.names = NULL)
      colnames(item.list[[i]]) <- colnames2
    } else {
      item.list[[i]] <- data.frame("Correct", item.sum[i],
                                   item.perc[i],
                                   item.tot.cor[i])
      colnames(item.list[[i]]) <- colnames1
    }
  }
  
  #Create item names
  names(item.list) <- item.names
  
  item.list
}

item.list <- CreateItemList(input.correct = input.correct, n.answer.op = n.answer.op, freq.answer.op = freq.answer.op, perc.answer.op = perc.answer.op, answer.op.tot.cor = answer.op.tot.cor, item.sum = item.sum, item.perc = item.perc, item.tot.cor = item.tot.cor)

# Use the function defined above

```

# General

 What | Result | Explanation of the tables |
:---------------------- | :------------- | :-----------------------
  Number of students| `r n.stud` |   For each question the frequency, percentage and item rest correlations (IRC)
Number of questions | `r n.item` |  from every answer option are diplayed. The IRC should be (highly) positive
Average score | `r round(mean(rowSums(input.correct)), digits = 3)`  | for the right answer option and low for the wrong answer option(s).
Standard deviation | `r round(sd(rowSums(input.correct)), digits = 3)`  | |
  Cronbach's alpha | `r cronbach`  | |
Standard error | `r round(sd(rowSums(input.correct) * sqrt(1 - cronbach)), digits = 3)` | |


# Item statistics

```{r pander, results = "asis", eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE}
# Create tables per item with frequency chosen, percentage chosen and the item-rest correlation. Correct answers are highlighted in bold
pander.table <- function(item.list, key){
  panderOptions('knitr.auto.asis', FALSE)
  for(i in 1:length(item.list))
  {if(any(key[,i] == 1)){
    
    # Change correct column
    item.list[[i]]$Correct = revalue(item.list[[i]]$Correct, c("Correct" = "X", "Incorrect" = ""))
    colnames(item.list[[i]])[1:3] <- c("Answer Option", "Frequency", "Percentage")
    
    emphasize.strong.rows(which(key[,i] == 1, arr.ind = TRUE))
    pander(item.list[i])
  } else {
    t <- item.list[i]
    rownames(t[[1]]) <- NULL
    pander(t)
  }
  }
}

pander.table(item.list, key)

```

\pagebreak

```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 11, results = 'asis'}
# Create a dataframe with only the correct statistics. This is used in the general item plots

CreateDf <- function(input.correct, item.sum, item.tot.cor, item.perc){ 
  correct.df <- data.frame(item = factor(colnames(input.correct), colnames(input.correct)), item.sum, item.tot.cor, item.perc , 
                           perc.col = ifelse(item.perc < 40, 0, ifelse(item.perc > 70, 1, 1/75 * item.perc - 7/30)),
                           # From 0 to 40 perc correct the bar is coloured red. From 40 till 70 colours go from .3 till .7 (orange till green-ish. From 70 till 100, bar is coloured green.
                           
                           irc.col = ifelse(item.tot.cor < 0, 0, ifelse(item.tot.cor > .1, 1, 4 * item.tot.cor + 3/10))
                           # Below 0 IRC, an item is colour red. Between 0 and .1 an item is coloured orange. Higher than .1 an item is coloured green.
  )
  
  t <- regexpr("\\d+", correct.df$item) ## Extract only numbers from item names
  correct.df$item <- factor(regmatches(correct.df$item, t), regmatches(correct.df$item, t))
  
  correct.df
}

correct.df <- CreateDf(input.correct = input.correct, item.sum = item.sum, item.tot.cor = item.tot.cor, item.perc = item.perc)



### Frequency Plot for total items
FreqPlotOverall <- function(correct.df){
  
  cat('

## Percentage Correct

Plot of percentage correct per item. If *more than 70%* of the students answer an item correctly, the students have mastered the material well enough, thus it is coloured *green*. If *less than 40%* of the students answer an item correctly, the students have not mastered the material, and is coloured *red*. *Orange* indicates the percentage correct lies *between 40% and 70%*. The boundaries of the colours are based on multiple choice items with 3 or 4 answer options.

')
  
  bar.freq <- ggplot(correct.df, aes(item, item.perc, fill = perc.col)) # Create chart with Answer Option on x-axis and percentae correct on y-asix
  bar.freq <-  bar.freq + geom_bar(stat = "identity") + # Create Bar chart
    scale_fill_gradient(low = "red", high = "green", limits = c(0, 1), guide = FALSE)  + # Create colour boundray: Green = "right" according to psychometrics, a value of 50% correct is ideal.
    coord_cartesian(ylim = c(0, 100)) + # Change y-axis limit to constant
    labs(x = "Item", y = "Percentage Correct") + #x axis name
    theme(strip.text.x = element_text(size = 7) , axis.text.x = element_text(size = 8), # Change font size of item names and Answer options
          axis.ticks.x = element_line(size = .4)) +
    theme_bw()
  
  suppressWarnings(print(bar.freq))
}

FreqPlotOverall(correct.df)

```

```{r, echo = FALSE, eval = TRUE, warning= FALSE, fig.width = 11, results = 'asis'}

IRCPlotOverall <- function(correct.df){
  cat('\\pagebreak

## Item rest correlations

Plot of Item Rest Correlations per item: The correlation between an item (0 for wrong answers and 1 for right answers) and the sum of all other items.
Items with a correlation *higher than .1* indicate that students who answered this item correctly answered the other items more often correctly than students who answered this item incorrectly. Thus it is coloured *green*. Items with a correlation *lower than 0* indicate no relationship between this item and the other items, thus it is coloured *red*. *Between 0 and .1*, an item is coloured *orange*.

')
  
  ### IRC Bar Plot for total items
  bar.IRC <- ggplot(correct.df, aes(item, item.tot.cor, fill = irc.col)) # Create chart with Answer_Option on x-axis and IRC on y-asix
  bar.IRC <-  bar.IRC + geom_bar(stat = "identity") + # Create Bar chart
    scale_fill_gradient(low = "red", high = "green", limits = c(0, 1), guide = FALSE)  + # Create colour boundray: Green = "right" (low for wrong answer options, high for right answer options)
    #    coord_cartesian(ylim = c(ifelse(min(correct.df$item.tot.cor < 0), min(correct.df$item.tot.cor), 0), 1)) + # Change y-axis limit to constant
    labs(x = "Item", y = "Item Rest Correlation") + # Change titles and x axis name
    theme(strip.text.x = element_text(size = 7), axis.text.x = element_text(size = 8), # Change font size of item names and Answer options
          axis.ticks.x = element_line(size = .4)) +
    theme_bw()
  
  suppressWarnings(print(bar.IRC))
}

IRCPlotOverall(correct.df)

```



```{r, echo = FALSE, eval = TRUE, warning= FALSE, fig.width = 11}

# Create extra variables for the colours in the bar plots
PercCol <- function(item.perc, Correct){
  # Calculate colours for the percentage answer options.
  #Args:
  # item.perc: Percentage answered per answer options
  # correct:   Vector of "Correct" and "Incorrect" of same length of item.perc
  #
  #Returns:
  # Value between 0 and 1 with 0 corresponding to red and 1 to green in the plots.
  # For the correct answers: lower than 40 returns 0, higher than 70 returns 1, and in between returns a scale from .3 till .7.
  # For the incorrect answers: difference between lowest correct answer option and incorrect answer options are calculated.
  # If the difference is bigger than 0, it returns 0. If difference is smaller than -10, it returns 1. In between returns a scale from .3 till .7.
  perc.col <- vector()
  perc.col[Correct == "Correct"] <- ifelse(item.perc[Correct == "Correct"] < 40, 0, ifelse(item.perc[Correct == "Correct"] > 70, 1, 3/200 * item.perc - 3/10))
  dif <- item.perc[Correct == "Incorrect"] - min(item.perc[Correct == "Correct"])
  perc.col[Correct == "Incorrect"] <- ifelse(dif >= 0, 0, ifelse(dif < -10, 1, -1/25 * dif + 3/10))
  return(perc.col)
}


IrcCol <- function(IRC, Correct){
  # Calculate colours for the percentage answer options.
  #Args:
  # IRC:     IRC per answer options
  # correct: Vector of "Correct" and "Incorrect" of same length of IRC
  #
  #Returns:
  # Value between 0 and 1 with 0 corresponding to red and 1 to green in the plots.
  # For the correct answers: lower than 0 returns 0, higher than .1 returns 1, and in between returns a scale from .3 till .7.
  # For the incorrect answers: difference between incorrect answer options and lowest correct answer option are calculated.
  # If the difference is bigger than 0, it returns 0. If difference is smaller than -.05, it returns 1. In between returns a scale from .3 till .7.
  IRC.col <- vector()
  IRC.col[Correct == "Correct"] <- ifelse(IRC[Correct == "Correct"] < 0, 0, ifelse(IRC[Correct == "Correct"] > .1, 1, 3 * IRC + 3/10))
  dif <- IRC[Correct == "Incorrect"] - min(IRC[Correct == "Correct"])
  IRC.col[Correct == "Incorrect"] <- ifelse(dif >= 0, 0, ifelse(dif < -.05, 1, -8 * dif + 3/10))
  return(IRC.col)
}


CreateAnsDf <- function(item.list){
  for(i in 1:length(item.list)) {
    if (any(key[, i] != 0)) {
      item.list[[i]]$perc.col <- with(item.list[[i]], PercCol(percentage, Correct))
      item.list[[i]]$IRC.col <- with(item.list[[i]], IrcCol(IRC, Correct))
      
    }
  }
  
  # Create data frame of all the items which have answer options. This is used to make barplots per answer option
  # Create right order on the x-axis (Correctness last)
  if (any(key != 0)) {
    ans.opt.df <- ldply(item.list[n.answer.op != 0], data.frame)
    names(ans.opt.df)[1] <- "id"
    ans.opt.df$answer.option <- gsub("Missing", "Mi", ans.opt.df$answer.option)
    ans.opt.df$answer.option <- factor(ans.opt.df$answer.option,
                                       levels = c(LETTERS[1 : max(n.answer.op)], "Mi"))
    ans.opt.df$id <- factor(ans.opt.df$id , levels = colnames(input.correct)[n.answer.op != 0])
  }
  if(!exists("ans.opt.df")){
    ans.opt.df <- NULL
  }
  ans.opt.df
}
ans.opt.df <- CreateAnsDf(item.list)

NumberOfPlots <- function(ans.opt.df){
  # Calculating which questions are displayed on which plot. The number of plots is determined by a max of 80 bars per plot and then dividing all answer options over the plot
  if (any(key != 0)) {
    max.answ.opts = 80
    tot.answ.opts = nrow(ans.opt.df)
    n.plots = ceiling(tot.answ.opts / max.answ.opts)
    answ.opts.per.plot = tot.answ.opts / n.plots
    
    items.in.plot <- list(unique(ans.opt.df[1 : answ.opts.per.plot, 1]))
    if(n.plots > 1){
      for(i in 2:n.plots)
        items.in.plot[[i]] <- unique(ans.opt.df[((i - 1) * answ.opts.per.plot) : (i * answ.opts.per.plot), 1])
      items.in.plot[[i]] <- items.in.plot[[i]][-1]
    }
    assign("n.plots", n.plots, envir=globalenv())
    assign("items.in.plot", items.in.plot, envir=globalenv())

  }
}

NumberOfPlots(ans.opt.df)
```



```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, fig.width = 11, results= 'asis'}    
# Create the plots of the frequencies per answer option
FreqPlotAnswOpt <- function(ans.opt.df, items.in.plot){
  if (any(key != 0)) {
    cat('\\pagebreak

## Percentage chosen per answer options

Percentage plot of all answer options per question. **White** bars represent the **right** answer option(s) and **black** the **wrong** options. 

The border represents the performance of an item. The **right** answer options are coloured *green* if *more than 70%* of the students choose this option. In that case, the students have mastered the material. They are coloured *red* if *less than 40%* choose this option. *Between 40% and 70%*, it is coloured *orange*.

The **wrong** answer options are coloured *green* if an option is chosen *10 percentage point less than the right option*. In that case, more students chose the right answer option than the wrong option indicating that students are not confused by the wrong option. They are coloured *red* if an option is chosen *equally or more often than the right option*. In this case, students pick the wrong answer option often, indicating that this option may be right as well. It is coloured *orange* in between these two.

')
    for(i in 1:length(items.in.plot)){ 
      bar.freq1 <- ggplot(ans.opt.df[ans.opt.df$id %in% items.in.plot[[i]], ],  # Select subset of questions
                          aes("Answer Option", percentage, fill = Correct, colour = perc.col)) # Create chart with Answer Option on x-axis and frequency on y-asix
      bar.freq1 <- bar.freq1 + geom_bar(aes(x = answer.option), stat = "identity", size = 1.5) + # Create Bar chart
        facet_grid(. ~ id, scales = "free_x", space = "free_x") + # Display the different items
        scale_fill_manual(values = c("Incorrect" = "Black" ,"Correct" = "White"), guide = FALSE) + # Fill in the bars: White for right answer options, Black for wrong answer options
        scale_colour_gradient(low = "red", high = "green", limits = c(0, 1), guide = FALSE)  + # Create colour boundray: Green = "right" (low for wrong answer options, high for right answer options)
        coord_cartesian(ylim = c(0, 100)) + # Change y-axis limit to constant
        labs(x = "Answer Options") + # x axis name
        theme_bw() + 
        theme(axis.text.x = element_text(size = 8), # Font size of text by tick marks of the x-asis
              axis.text.y = element_text(size = 12), # Font size of text by tick marks of the x-asis
              axis.title.x = element_text(size = 15), # Font size of the x-asis title
              axis.title.y = element_text(size = 15) # Font size of the y-axis title 
        ) 
      
      suppressWarnings(print(bar.freq1))
    }
  }
}

FreqPlotAnswOpt(ans.opt.df, items.in.plot)

```



```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, results = 'asis', fig.width = 11}

IRCPlotAnswOpt <- function(ans.opt.df, items.in.plot){
  if (any(key != 0)) {
    
    cat('\\pagebreak

## Item rest correlations per answer option

Item rest correlation (IRC) plot of all answer options per question. The IRC is the correlation between an answer option (1 for students who chose this options and 0 for student who did not) and the sumscore on all other items. **White** bars represent the **right** answer option(s) and **black** the **wrong** options. 

The border represents the performance of an item. The **right** answer options are coloured *green* if the IRC is *higher than .1*. In that case, students who picked the right answer option scored higher on all other items than student who did not pick the right option. They are coloured *red* if the IRC is *less than 0*. In that case, students who picked the right answer option scored equally or worse on the other items than students who picked the other options. Between *0 and .1*, the option is coloured *orange*.

The **wrong** answer options are coloured *green* if the IRC is *more than .1 lower than the right option*. In that case, students who answered the other items incorrectly, usually answered this item incorrectly as well. They are coloured *red* if the IRC is *equal or higher than the right answer option*. In that case, students who answered the other items correctly may have answered this item incorrectly. In between these two, the option is coloured *orange*.

')
    
    # Creating IRC plots 
    for(i in 1:length(items.in.plot)){ 
      bar.IRC1 <- ggplot(ans.opt.df[ans.opt.df$id %in% items.in.plot[[i]], ]  # Select subset of first plots
                         , aes("Answer Option", IRC, fill = Correct, colour = IRC.col)) # Create chart with Answer Option on x-axis and IRC on y-asix
      bar.IRC1 <-  bar.IRC1 + geom_bar(aes(x = answer.option), stat = "identity", size = 1.5) + # Create Bar chart
        facet_grid(. ~ id, scales = "free_x", space = "free_x") + # Display the different items
        scale_fill_manual(values = c("Incorrect" = "Black" ,"Correct" = "White"), guide = FALSE) + # Fill in the bars: White for right answer options, Black for wrong answer options
        scale_colour_gradient(low = "red", high = "green", limits = c(0, 1), guide = FALSE)  + # Create colour boundray: Green = "right" (low for wrong answer options, high for right answer options)
        coord_cartesian(ylim = c(ifelse(min(ans.opt.df$IRC) < -.3, min(ans.opt.df$IRC) - .01, -.3),
                                 ifelse(max(ans.opt.df$IRC) > .4, max(ans.opt.df$IRC) + .01, .4))
        ) + # Change y-axis limit to either the maximum IRC or .4 and minimum IRC or -.3
        labs(x = "Answer Options") + #x axis name
        theme_bw() + 
        theme(axis.text.x = element_text(size = 8), # Font size of text by tick marks of the x-asis
              axis.text.y = element_text(size = 12), # Font size of text by tick marks of the x-asis
              axis.title.x = element_text(size = 15), # Font size of the x-asis title
              axis.title.y = element_text(size = 15) # Font size of the y-axis title 
        ) 
      
      suppressWarnings(print(bar.IRC1))
    }
  }
}

IRCPlotAnswOpt(ans.opt.df, items.in.plot)
```

\pagebreak

## Cumulative Distribution

Cumulative Distribution showing all possible scores and the percentage of students that scored that number or higher

```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, fig.width = 11}
# Create cumulative histogram

CumHist <- function(input.correct){
  totaal <- rowSums(input.correct)
  heights <- length(totaal)
  h = heights[1]
  
  n <- sort(unique(totaal))
  
  for(i in 1:length(n))
  {
    h = h - length(totaal[totaal == n[i]])
    heights = c(heights, h)
  }
  
  cesuurlijnen <- seq(0.2, 0.8, 0.2) * nrow(input.correct)
  gridlijnen <- round(seq(0, nrow(input.correct), (nrow(input.correct)/25)), 0)
  
  gridlijnen <- gridlijnen[-grep(paste(cesuurlijnen, collapse = "|"), gridlijnen)]
  
  heights <- heights[1:length(unique(totaal))]
  percent <- heights/length(totaal)*100
  df <- data.frame(score = sort(unique(totaal)), total = heights, percent = round(percent,2))
  
  h <- ggplot(data = df, aes(x = score, y = total)) + 
    geom_hline(yintercept = c(gridlijnen), linetype = "solid", colour = "gray80") +  
    geom_hline(yintercept = cesuurlijnen, linetype = "dashed", size = 0.75, colour = "black") +
    geom_histogram(stat = "identity", binwidth = 1) + 
    xlab("Total score") + ylab("% students with score or higher") + 
    scale_y_continuous(breaks = c(0, cesuurlijnen, nrow(input.correct)), labels = c(seq(0, 100, 20))) +
    scale_x_continuous(limits = c((df[1,1]-1), ncol(input.correct)), breaks = 1:ncol(input.correct), expand=c(0,0)) + 
    theme_bw() +
    theme(panel.grid = element_blank())
  
  print(h)
}

CumHist(input.correct)

```


```{r, echo = FALSE, eval = TRUE, warnings = FALSE, message = FALSE, results = 'asis', fig.width = 11}
## Do the whole script above for every sub category
if(is.list(results[[1]])){
  for(sub in 2:length(results)){
    
    cat('\\pagebreak

        ')
    
    cat(paste('
              
# Category', sub - 1 ), '
        
        ')
    
    retrieve(results, n = sub, sub.cat = TRUE) # Get objects in list to global environment
    
    item.list <- CreateItemList(input.correct = input.correct, n.answer.op = n.answer.op, freq.answer.op = freq.answer.op, perc.answer.op = perc.answer.op, answer.op.tot.cor = answer.op.tot.cor, item.sum = item.sum, item.perc = item.perc, item.tot.cor = item.tot.cor)
    
    correct.df <- CreateDf(input.correct = input.correct, item.sum = item.sum, item.tot.cor = item.tot.cor, item.perc = item.perc)
    

    FreqPlotOverall(correct.df)

    IRCPlotOverall(correct.df)
    
    ans.opt.df <- CreateAnsDf(item.list)
    NumberOfPlots(ans.opt.df)
    
    FreqPlotAnswOpt(ans.opt.df, items.in.plot)
    
    IRCPlotAnswOpt(ans.opt.df, items.in.plot)
    
    cat('\\newpage')
    cat('\n\n')
    cat('## Cumulative Distribution')
    cat('\n\n')
    CumHist(input.correct)

  }
}

```
